PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-09-12 qfenv_paper/qf_environment.tex
not-noteworthy changes

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
large fraction of the decline is associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fractions of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\citealt{Blanton:2006aa, bundy06a, borch06a, Moustakas:2013aa}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \citet{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

@@

In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our mass complete sample construction, and galaxy environment measurements. After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples. In Section \ref{sec:qf_const}, we calculate the quiescent fraction and compare the evolution of the quiescent fraction between high and low density environments. In Section \ref{sec:discussion} we discuss the trends observed in the stellar mass function and quiescent fraction evolution and discuss implications of the results on quenching mechanisms. Finally in Section \ref{sec:summary} we summarize our results.

>>>>

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
large fraction of the decline is associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fractions of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\citealt{Blanton:2006aa, bundy06a, borch06a, Moustakas:2013aa}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \cite{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

@@

In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our mass complete sample construction, and galaxy environment measurements. After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples in Section \ref{sec:smf}. Afterwards, in Section \ref{sec:qf_const}, we calculate the quiescent fraction, analyze the evolution of the quiescent fraction, quantify the effects of environment on the quiescent fraction evolution, and discuss the implications of our quiescent fraction results on star-formation quenching. Finally in Section \ref{sec:summary} we summarize our results.
